%%
%% This is file `squelette-rr.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% RR.dtx  (with options: `sample')
%% ********************************************************************
%% Copyright (C) 1997-1999 2004 2006-2011 INRIA/APICS/MARELLE by Jose' Grimm
%% This file may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License, either version 1.3
%% of this license or (at your option) any later version.
%% The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.3 or later is part of all distributions of LaTeX
%% version 2003/12/01 or later.
%% An archive of the software can be found at
%%    ftp://ftp-sop.inria.fr/marelle/RR-INRIA

\documentclass[twoside]{article}
\usepackage[a4paper]{geometry}
\usepackage[utf8]{inputenc} % use UTF-8 input encoding
\usepackage[T1]{fontenc} % ou \usepackage[OT1]{fontenc}
\usepackage{RR}
\usepackage{hyperref}
\usepackage{bookmark} % improve outline handling, avoids rerun warnings
\usepackage[norule]{footmisc} % pour supprimer le filet des notes
%%\usepackage[frenchb]{babel} % optionnel
\RRNo{XXXX}
%% \RTNo{0703}
%%
%% date de publication du rapport
\RRdate{MONTH YEAR}
%%
%% Cas d'une version deux
%% \RRversion{2}
%% date de publication de la version 2
%% \RRdater{November 2008}
%%\RRversion{2\thanks{la note explicative}}
\RRdater{MONTH YEAR} % date de revision du rapport
\RRauthor{% les auteurs
 % Premier auteur, avec une note
Alexandre Lou-Poueyou\thanks{Computer Science Master's Degree Student at University of Bordeaux - Intern at TADaaM team}%
 % \and entre chaque auteur s'il y en a plusieurs
  \and
Francieli Boito\thanks{Associate Professor at University of Bordeaux \& permanent researcher at TADaaM team}%
 % r\'ef\'erence \`a la note partag\'ee
 % liste longue pour tests de mise en page
\and Meline Trochon\thanks{PhD stutent at TADaaM team} \and Luan Teylo \thanks{Permanent researcher at TADaaM team}}
%% Ceci apparait sur chaque page paire.
\authorhead{Alexandre \& Francieli \& others}
%% titre francais long
\RRtitle{Exemple de document\\
 utilisant le style\\rapport de recherche\\Inria}
%% English title
\RRetitle{Improving I/O Performances of HPC Application Gysela}
%%
\titlehead{Improving I/O performances of HPC Application Gysela}
%%
%\RRnote{This is a note}
%\RRnote{This is a second note}
%%
\RRresume{Ce document montre comment utiliser le style RR.sty.
Pour en savoir plus, consulter le fichier RR.dvi ou RR.pdf.
D\'efinissez toujours les commandes avant utilisation.
}
\RRabstract{
In modern High Performances Computing's (HPC) systems, Input/Output (I/O) 
performances are often a limiting factor for large scale scientifics simulations.
Since supercomputer power et data volume keep increasing, I/O performance optimization
becomes essential in order to efficiently exploit available ressources. In this context,
scientifics's applications are largely based on Parallel Files System (PFS) enabling the
access at the same time to very large amount of datas. However, the results achieved highly
depends of many configuration's parameters as well as grounds for accessing the data used by
applications. Understanding and Optimizing those interactions constitues a crucial issue for
improving HPC simulations global efficiency.\\ 
This work is part of the optimization of I/O performances of the application called Gysela, 
a simulation code developped by CEA for the study of plasma's turbulences in Tokamak, for the 
study of nuclear fusion. Those simulations produce large amount of datas and needed regular checkpoints 
writing, that allow to save the state of the simulation it can resume it in case of an interruption, 
whether it is due to a hardware failure or a limitation on the allotted processing time on supercomputers.
}
\RRkeyword{HPC, Parallel I/O, Performances Tuning, Parallel File Systems}
%%
%% \RRprojet{Apics}  % cas d'un seul projet
\RRprojets{TADaaM}
%%
%% \URLorraine % pour ceux qui sont \`a l'est
%% \URRennes  % pour ceux qui sont \`a l'ouest
%% \URRhoneAlpes % pour ceux qui sont dans les montagnes
%% \URRocq % pour ceux qui sont au centre de la France
%% \URFuturs % pour ceux qui sont dans le virtuel
%% \URSophia % pour ceux qui sont au Sud.
%%
%% \RCBordeaux % Centre Inria de l'Université de Bordeaux
%% \RCGrenoble % Centre Inria de l'Université de Grenoble Alpes
%% \RCLille % Centre Inria de l'Université de Lille
%% \RCLyon % Centre Inria de Lyon
%% \RCNancy % Centre Inria de l'Université de Lorraine
%% \RCParis % Centre Inria de Paris
%% \RCRennes % Centre Inria de l'Université de Rennes 
%% \RCSaclay % Centre Inria de Saclay
%% \RCSophia % Centre Inria d'Université Côte d'Azur


\RCBordeaux

%%
\begin{document}
%%
%\makeRR   % cas d'un rapport de recherche
\makeRT % cas d'un rapport technique.
%% a partir d'ici, chacun fait comme il le souhaite
\tableofcontents \newpage

\section{Introduction}
\label{sec1}

The growing gap between computational performance and I/O capabilities in modern HPC
systems has become a critical concern for large-scale scientific simulations. 
As supercomputers approach exascale, applications generate ever-increasing volumes of data, 
making efficient data management essential for both performance and fault tolerance. 
Among the various I/O patterns found in scientific codes, checkpointing—the periodic saving of 
simulation state to enable job restart after failures or time limits—is particularly demanding, 
as it involves writing large amounts of data in a short time window.\\

\section{Second section}
Text for the second section. This is closely related to the text in
section \ref{sec1} on page \pageref{sec1}. \newpage

% Bibliography style (none used in this template, but ensures \bibstyle is set)
\bibliographystyle{plain}

\end{document}
\endinput
%%
%% End of file `squelette-rr.tex'.
